---
title: "Brief"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width=10, fig.height=7)
options(width = 100)

library(tidyverse)

gsave <- F

```

```{r, include=FALSE, cache = T, echo = F}
load("Results/Brief/out.rdata")

results <- bind_rows(out.i) %>%
  ungroup() %>%
  mutate(Est_Equal = ifelse(isEqual, "Equal", "Unequal"),
         Est_Random = ifelse(isRandom, "Random", "Fixed"),
         Gen = ifelse(Gen == "Y_EQ", "Equal", "Unequal"),
         Correct = (Est_Equal == Gen & Est_Random == "Random"),
         Correct = ifelse(Correct, T, NA),
         Parameter = factor(Parameter),
         Bs = factor(Bs),
         ICC = factor(round(ICC, 2)),
         X_PS.cor = factor(X_PS.cor),
         M.m = factor(M.m))

levels(results$Parameter) <- c("FE_Int", "FE_M", "FE_Mj", "FE_Xj", "FE_X", "RE_e", "RE_u")
results$Parameter <- factor(results$Parameter, c("FE_Int", "FE_M", "FE_X", "FE_Mj", "FE_Xj", "RE_e", "RE_u"))


levels(results$Bs) <- c("{gamma['01']==gamma['02']}==.5", "{gamma['01']==gamma['02']}==1")
levels(results$X_PS.cor) <- paste("rho[XM]==", levels(results$X_PS.cor), sep = "")
levels(results$ICC) <- paste("ICC==", levels(results$ICC), sep = "")
levels(results$M.m) <- paste("bar(M)==", levels(results$M.m), sep = "")
```

## Data Generation

### Fixed

  + Students
    * 3000
  + Schools
    * 100
  + Pretest
    * ~ N(0,1)
  + L1 Coefficients
    * Intercept = 0
    * Mobility = 1
    * Pretest = 1
  + Error
    * ~ N(0,1)
  

### Manipulated

  + p_{X,M}
    * 0
    * .25
    * .5
  + Mobility %
    * .1
    * .25
  + ICC
    * .15
    * .25
  + L2 Coefficients
    * Mobility = .5, 1
    * Pretest = .5, 1
  
  


## Results


### Collapse across conditions

There is some variation due to conditions but on average the different estimation methods do not seem to have much difference

```{r, cache = T, echo = F, fig.width=10, fig.height=7}

df_sum <- results %>% filter(stat == "Estimate")
# df_sum <- results %>% filter(stat == "Error")


df_sum %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "RPB - All Conditions") +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-All Cond.jpg", dpi = 1000, width = 11, height = 8.5)


```

### RPB for each parameter across conditions

L1 fixed effects perform well with no apparent differences by weight and will be dropped for the remainder.

$\sigma$ is estimated well but left in. Notably this is the only parameter where correct weight specification consistantly outperforms

$\gamma_{M_j}$ displays substantial bias. 

```{r, cache = T, echo = F}
df_sum %>%
  arrange(Parameter) %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "RPB - All Conditions by Parameter") +
  facet_wrap(~ Parameter, scales = "free_y", labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-Cond by Param.jpg", dpi = 1000, width = 11, height = 8.5)
```

### RPB for each parameter by $\rho_{X,M}$

Bizarre relationship between $\rho$ and $\gamma_{M_j}$ bias

```{r, cache = T, echo = F}

df_sum2 <- df_sum %>% filter(Parameter %in% c("FE_Mj", "FE_Xj", "RE_u"))

df_sum2 %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "RPB - X_M Cor by Parameter") +
  facet_grid(Parameter ~ X_PS.cor, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-X_M Cor by Parameter.jpg", dpi = 1000, width = 11, height = 8.5)

# df_sum2 %>%
#   filter(Parameter == "FE_Mj") %>%
#   ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
#   geom_boxplot() +
#   geom_hline(yintercept = 0) +
#   geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
#   # labs(title = "RPB - X_M Cor by Parameter") +
#   facet_grid(Parameter ~ X_PS.cor) +
#   scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
#   scale_color_brewer(type = "qual", palette = 2) +
#   theme_minimal() +
#   labs(x = "Generating Weights", y = "RPB") +
#   theme(legend.position = "right",
#         panel.spacing = unit(2, "lines"),
#         text = element_text(size=20),
#         legend.title = element_text(size=15)) +
#   guides(color = guide_legend(title = ""),
#          linetype = guide_legend(title = "Estimating Weights"))
# 
# if(gsave) ggsave("Figs/RPB-X_M Cor by Parameter-Mj only.jpg", dpi = 1000, width = 11, height = 8.5)

```

### RPB for each parameter by mobility %

$\gamma_{M_j}$seem biased with low mobility

Unequal weights result in biased $\gamma_{Y_j}$ and $\tau_{00}$ when true weights are equal

For some reason Fixed and Random Unequal weights seem to diverge from other models here for $\tau_{00}$ and $\gamma_{X_j}$

```{r, cache = T, echo = F}

df_sum2 %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "RPB - %M by Parameter") +
  facet_wrap(Parameter ~ M.m, ncol = 2, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-Prec M by Parameter.jpg", dpi = 1000, width = 11, height = 8.5)

```

### RPB for each parameter by ICC

Larger ICC increases variability of $\gamma_{M_j}$ across other conditions, bias increased on average

Again Fixed and Random Unequal weights diverge  under equal weight generation condition

```{r, cache = T, echo = F}


df_sum2 %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "RPB - ICC by Parameter") +
  facet_wrap(Parameter ~ ICC, ncol = 2, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-ICC by Parameter.jpg", dpi = 1000, width = 11, height = 8.5)




```


### RPB for each parameter by L2 effects

Note: "Strong" $\gamma_{M_j} = \gamma_{X_j} = 1$; "Weak" $\gamma_{M_j} = \gamma_{X_j} = .5$

Again Fixed and Random Unequal weights diverg

```{r, cache = T, echo = F}
df_sum2 %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  labs(title = "RPB - L2 effects by Parameter") +
  facet_wrap(Parameter ~ Bs, ncol = 2, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/RPB-L2 effects by Parameter.jpg", dpi = 1000, width = 11, height = 8.5)
```

### $\gamma_{M_j}$

```{r, cache = T, echo = F}

df_sum %>%
  filter(Parameter == "FE_Mj") %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "FE_Mj RPB - %M by cor(X,M)") +
  facet_grid(X_PS.cor ~ M.m, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/FE_Mj RPB-Perc M by Cor.jpg", dpi = 1000, width = 11, height = 8.5)
```

```{r, cache = T, echo = F}

df_sum %>%
  filter(Parameter == "FE_Mj") %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "FE_Mj RPB - %M by L2 Strength") +
  facet_grid(X_PS.cor ~ Bs + M.m, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/FE_Mj RPB-Perc M by L2 and Cor.jpg", dpi = 1000, width = 11, height = 8.5)

```

```{r, cache = T, echo = F}

df_sum %>%
  filter(Parameter == "FE_Mj") %>%
  ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) +
  geom_boxplot() +
  geom_hline(yintercept = 0) +
  geom_hline(yintercept = c(.05, -.05), linetype = "dashed") +
  # labs(title = "FE_Mj RPB - %M by L2 Strength") +
  facet_grid(Bs + ICC ~ M.m, labeller = label_parsed) +
  scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) +
  scale_color_brewer(type = "qual", palette = 2) +
  theme_minimal() +
  labs(x = "Generating Weights", y = "RPB") +
  theme(legend.position = "right",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20),
        legend.title = element_text(size=15)) +
  guides(color = guide_legend(title = ""),
         linetype = guide_legend(title = "Estimating Weights"))

if(gsave) ggsave("Figs/FE_Mj RPB.jpg", dpi = 1000, width = 11, height = 8.5)

```

<!-- ```{r, cache = T, echo = F} -->

<!-- # df_sum %>% -->
<!-- #   filter(Parameter == "FE_Mj") %>% -->
<!-- #   ggplot(aes(x = Gen, y = RPB, color = Est_Equal, linetype = Est_Random, fill = Correct)) + -->
<!-- #   facet_grid(ICC + X_PS.cor ~ Bs + M.m, labeller = label_parsed) -->

<!-- df_sum %>% -->
<!--   filter(Parameter == "FE_Mj", Gen == "Equal") %>% -->
<!--   mutate(Correct = ifelse(is.na(Correct), FALSE, TRUE)) %>% -->
<!--   ggplot(aes(x = M.m, y = RPB, color = Correct)) + -->
<!--   geom_boxplot() + -->
<!--   geom_hline(yintercept = 0) + -->
<!--   geom_hline(yintercept = c(.05, -.05), linetype = "dashed") + -->
<!--   # labs(title = "FE_Mj RPB - %M by L2 Strength") + -->
<!--   facet_grid(Bs + ICC ~ Est_Equal + Est_Random, labeller = label_parsed) + -->
<!--   scale_fill_brewer(type = "seq", palette = 1, guide=FALSE) + -->
<!--   scale_color_brewer(type = "qual", palette = 2) + -->
<!--   theme_minimal() + -->
<!--   labs(x = "Generating Weights", y = "RPB") + -->
<!--   theme(legend.position = "right", -->
<!--         panel.spacing = unit(2, "lines"), -->
<!--         text = element_text(size=20), -->
<!--         legend.title = element_text(size=15)) + -->
<!--   guides(color = guide_legend(title = ""), -->
<!--          linetype = guide_legend(title = "Estimating Weights")) -->

<!-- if(gsave) ggsave("Figs/FE_Mj RPB", dpi = 1000, width = 11, height = 8.5) -->

<!-- ``` -->

