---
title: "Brief"
output: 
  html_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, fig.width=10, fig.height=7)
options(width = 100)

```

```{r, include=FALSE, cache = F, echo = F}
rm(list = ls())

source("SimSource.R")
# detach("package:R2MLwiN", unload=TRUE)
# library(dplyr)


```

## Curent Weight Distributions



```{r, cache = T, echo = F, fig.width=10, fig.height=7, warning = F}
df <- gen_data(n.students = 10000, 
               X_PS.cor = 0, 
               X.m = 0, 
               X.sd = 1, 
               M.m = .25, 
               e.m = 0, 
               e.sd = 1, 
               tripleRate = .3, 
               n.schools = 100, 
               u0.m = 0, 
               u0.sd = .5, 
               genMod = list(frm = ~ 1 + X + M + wMj + wXj + w.u0 + e, Bs = c(0,1,1,1,1,1,1)), 
               gmc = T,
               w.sd = 1)

df_w <- df %>%
  select(ID, w1:w3, nSchools, M, isRandom, isEqual) %>%
  gather(key = time, value = weight, w1:w3) %>%
  mutate(wType = paste(ifelse(isRandom, "Ran", "Fix"), ifelse(isEqual, "Eq", "Un"), sep = "_")) %>%
  select(-isRandom, -isEqual) %>%
  spread(key = wType, value = weight)


```

The current weight distributions give quite a bit of overlap for the equal weights condition, but not for the unequal weights. This may explain why EQ performs reasonably well (on average) when the generating weights are unequal, but not vice versa. This was actually one of my  critiques of previous studies, but my original fix didn't go far enough. This plot shows the weight distributions across number of schools (1, 2, 3) by time points (w1, w2, w3)


```{r, cache = F, echo = F, fig.width=10, fig.height=7}

# df_w %>%
#   ggplot(aes(x = Ran_Eq, y = Ran_Un)) +
#   geom_point(alpha = .5) +
#   facet_grid(nSchools~time)
```


```{r, cache = F, echo = F, fig.width=10, fig.height=7}
df %>%
  select(ID, w1:w3, nSchools, M, isRandom, isEqual) %>%
  gather(key = time, value = weight, w1:w3) %>%
  mutate(wType = paste(ifelse(isRandom, "Ran", "Fix"), ifelse(isEqual, "Eq", "Un"), sep = "_")) %>%
  select(-isRandom, -isEqual) %>%
  filter(str_detect(wType, "Ran")) %>%
  ggplot(aes(x = weight, color = wType)) +
  geom_density() +
  facet_grid(nSchools~time)
```


## Proposed Solution



```{r, cache = T, echo = F, fig.width=10, fig.height=7, warning = F}
df2 <- gen_data(n.students = 10000, 
               X_PS.cor = 0, 
               X.m = 0, 
               X.sd = 1, 
               M.m = .25, 
               e.m = 0, 
               e.sd = 1, 
               tripleRate = .3, 
               n.schools = 100, 
               u0.m = 0, 
               u0.sd = .5, 
               genMod = list(frm = ~ 1 + X + M + wMj + wXj + w.u0 + e, Bs = c(0,1,1,1,1,1,1)), 
               gmc = T,
               w.sd = .5)

df2_w <- df2 %>%
  select(ID, w1:w3, nSchools, M, isRandom, isEqual) %>%
  gather(key = time, value = weight, w1:w3) %>%
  mutate(wType = paste(ifelse(isRandom, "Ran", "Fix"), ifelse(isEqual, "Eq", "Un"), sep = "_")) %>%
  select(-isRandom, -isEqual) %>%
  spread(key = wType, value = weight)

```

Narrowing the distribution that we sample the weights from creates less overlap for both groups. This might not be equal, i.e. one group might still be more "representative" of the other, but we should see a decease in the performance of equal weights under the unequal generating conditions.

```{r, cache = F, echo = F, fig.width=10, fig.height=7}


# df2_w %>%
#   ggplot(aes(x = Ran_Eq, y = Ran_Un)) +
#   geom_point(alpha = .5) +
#   facet_grid(nSchools~time)
```


```{r, cache = F, echo = F, fig.width=10, fig.height=7}
df2 %>%
  select(ID, w1:w3, nSchools, M, isRandom, isEqual) %>%
  gather(key = time, value = weight, w1:w3) %>%
  mutate(Generation = paste(ifelse(isRandom, "Random", "Fixed"), ifelse(isEqual, "Equal", "Unequal"), sep = " ")) %>%
  select(-isRandom, -isEqual) %>%
  group_by(time, nSchools) %>%
  filter(str_detect(Generation, "Random"),
         sd(weight) != 0) %>%
  ungroup() %>%
  mutate(nSchools = paste("Attended", nSchools, "schools")) %>%
  ggplot(aes(x = weight, color = Generation)) +
  geom_density() +
  facet_grid(time~nSchools) +
  theme_minimal() +
  scale_color_brewer(type = "qual", palette = 2) +
  labs(x = "Value", y = "Density") +
  theme(legend.position = "bottom",
        panel.spacing = unit(2, "lines"),
        text = element_text(size=20))

ggsave("Dist of Weights.jpg", dpi = 1000, width = 11, height = 8.5)
```
